Effects of pre-existing structures on the seismicity of the Charlevoix Seismic Zone

### 2019-06-27 main_full_manuscript.tex
Update main_full_manuscript.tex

For simplicity, we assume that the \change[OF]{crater}{impact structure}'s bulk and shear moduli are a certain fraction of those of the crust~\citep[e.g.,][]{Baird_2010}. Similarly, the density of the \change[OF]{crater}{impact structure} is reduced by 10 \% from that of the 1D velocity models over the corresponding depth range \add[OF]{to model a damaged crustal rock but the model results were insensitive to other amounts of reduction as seen in Fig. S3 in the supplementary information.}

>>>>

For simplicity, we assume that the \change[OF]{crater}{impact structure}'s bulk and shear moduli are a certain fraction of those of the crust~\citep[e.g.,][]{Baird_2010}. Similarly, the density of the \change[OF]{crater}{impact structure} is reduced by 10 \% from that of the 1D velocity models over the corresponding depth range \add[OF]{to model a damaged crustal rock, but the model results were insensitive to other amounts of reduction as seen in Fig. S3 in the supplementary information.}
